### 2023-02-13 article.tex
Use '\abstract' (instead of '\abstract*')
Make cite look correct, fix #11
Make figure 1 bigger, fix #9

\setcounter{chapter}{7}
\chapter{How to make research code useful paradata}

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{figure_1.png}
  \caption{
    Left: general relation between data, paradata and metadata.
    Right: the same relations specified for genetic epidemiology.
  }
  \label{fig:figure_1}
\end{figure}

>>>>

\chapter{How to make research code useful paradata}

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{figure_1.png}
  \caption{
    \textbf{Left}: general relation between data, paradata and metadata.
    \textbf{Right}: the same relations specified for genetic epidemiology.
    Input data: genetic data, phenotypic data and associations
    found in earlier studies.
    Results: associations between genetic data and phenotypic data.
    Code: the computer code used in a computational experiment
    Paper: the scholarly paper describing the (code of the) experiment
  }
  \label{fig:figure_1}
\end{figure}
